\plaintitle

### 2017-06-05 papers/IoT2017/intro.tex
no message

In this paper, we propose a system that enables trading energy futures in a secure and verifiable manner, preserves the prosumers' privacy, and enables the DSO to regulate the trading platform and enforce certain safety rules.
\todo{Since SIGCHI does not have section numbers, this paragraph, which describes the organization of the paper, is not very clear.}
First, we describe the basic elements of a transactive microgrid, and we formulate security, safety, and privacy requirements. 
Then, we introduce a decentralized system for transactive microgrids based on distributed ledgers, and describe in detail the transactions and services that are used to implement this system.
Next, we discuss how the system satisfies the security, safety, and privacy requirements.
Finally, we give a brief overview of related work and offer concluding remarks.

>>>>

In this paper, we propose a system that enables trading energy futures in a secure and verifiable manner, preserves the prosumers' privacy, and enables the DSO to regulate the trading platform and enforce certain safety rules.
\Aron{Since SIGCHI does not have section numbers, this paragraph, which describes the organization of the paper, is not very clear.}
First, we describe the basic components of a transactive microgrid, and we formulate security, safety, and privacy requirements. 
Then, we introduce a decentralized system for transactive microgrids based on distributed ledgers, and describe in detail the transactions and services that are used to implement this system.
Next, we discuss how the system satisfies the security, safety, and privacy requirements.
Finally, we give a brief overview of related work and offer concluding remarks.

### 2017-06-05 papers/IoT2017/prelim.tex
no message

\subsubsection{Microgrid Controller}
The microgrid controller is responsible for stabilizing load within the microgrid and controlling it based on the expected load in the rest of the grid.
To this end, the controller first estimates the expected load in the microgrid based on the bids and asks in the bid storage as well as on outstanding energy trades in the ledger.
By combining this estimate with the expected load in the remainder of the grid, the controller produces a control signal that specifies how much the microgrid load should be decreased or increased.
Finally, based on this control signal, the controller updates the price policy for the microgrid to influence energy production and consumption.

@@

\subsection{Requirements}
Next, we discuss the security, safety, and privacy requirements that must be satisfied by a transactive energy system.

\subsubsection{Security}
Security requirements primarily ensure that every prosumer is billed correctly, but they also provide necessary prerequisite properties for safety.
%Prosumers (or outside attackers) should not be able to tamper with measured energy production and consumption values, with financial balances, with other prosumers' bids.
More specifically, we require that 
\begin{compactitem}
\item prosumers are billed correctly based on the energy prices set by the DSO, their energy trades, and their energy production and consumption measured by the smart meters (i.e., energy production and consumption measurements and financial balances cannot be tampered with),
\item prosumers or outside attackers cannot change microgrid policies that are to be set by the DSO,
\item prosumers cannot back out of trades unilaterally, and they cannot tamper with other prosumers' trading and bidding,
\item financial and physical impact of a compromised or faulty node is limited, and the node can be banned by the DSO.
\end{compactitem}

>>>>

\subsubsection{Microgrid Controller}
The microgrid controller is responsible for stabilizing load within the microgrid and controlling it based on the expected load in the rest of the grid.
To this end, the controller first estimates the expected load in the microgrid based on the bids and asks in the bid storage as well as on outstanding energy trades in the ledger.
By combining this estimate with the expected load in the remainder of the grid, the controller produces a control signal that specifies how much the microgrid load should be decreased or increased.
Finally, based on this control signal, the controller updates the price policy for the microgrid to influence energy production and consumption.
\Abhishek{Mention that we assume the presence of a secondary controller that balances the voltage and frequency in the microgrid.}

@@

\subsection{Requirements}
Next, we discuss the security, safety, and privacy requirements that must be satisfied by a transactive energy IoT system.

\subsubsection{Security}
Security requirements primarily ensure that every prosumer is billed correctly, but they also provide necessary prerequisite properties for safety.
%Prosumers (or outside attackers) should not be able to tamper with measured energy production and consumption values, with financial balances, with other prosumers' bids.
More specifically, we require that 
\begin{compactitem}
\item prosumers are billed correctly based on the energy prices set by the DSO, their energy trades, and their energy production and consumption measured by the smart meters (i.e., energy production and consumption measurements and financial balances cannot be tampered with),
\item prosumers or outside attackers cannot change microgrid regulatory policies that are set by the DSO,
\item prosumers cannot back out of trades unilaterally, and they cannot tamper with other prosumers' trading and bidding,
\item financial and physical impact of a compromised or faulty node is limited, and the node can be banned by the DSO.
\end{compactitem}

### 2017-06-05 papers/IoT2017/services.tex
no message

In this subsection, we describe the services on which transactions are built and which build on transactions.
We have already discussed distributed ledgers, which permanently store transactions.
Now, we will introduce anonymous communication service, mixing service for transaction anonymity, anonymous bid storage, and billing.\todo{Revise list based on final organization!}

@@

@@

\subsubsection{Billing and Microgrid Control}

>>>>

In this subsection, we describe the services on which transactions are built and which build on transactions.
We have already discussed distributed ledgers, which permanently store transactions.
Now, we will introduce anonymous communication service, mixing service for transaction anonymity, anonymous bid storage, and billing.\Aron{Revise list based on final organization!}

@@

% discuss three approaches:
% - third-party based services: not really suitable
% - decentralized protocols: can work
``In this paper we propose CoinShuffle, a completely decentralized Bitcoin mixing protocol that allows users to utilize Bitcoin in a truly anonymous manner. ''~\cite{ruffing2014coinshuffle}
``As a solution, we propose Xim, a two-party mixing protocol that is compatible with Bitcoin and related virtual currencies.''~\cite{bissias2014sybil}
% - cryptographic anonymity (buit-in)
% Zerocoin

@@

\subsubsection{Billing}

### 2017-06-05 papers/IoT2017/solution.tex
no message

At this point, the production asset can still be traced back to the prosumer since the ledger is public.
To achieve anonymity, the prosumer transfers the production asset to a \emph{mixing service} using an \emph{energy and financial transaction} \circled{2}, which is also recorded on the distributed ledger.
In turn, the mixing service transfers the production asset to an \emph{anonymous address} \circled{3}\todo{We should probably insert a good definition here for readers who are unfamiliar with blockchain transactions.}, which is randomly generated and controlled by the prosumer.
Since the mixing service transfers assets from multiple prosumers to multiple anonymous addresses at the same time, and the anonymous addresses were chosen at random by the prosumers, the assets cannot be traced back to the original prosumers after mixing.\footnote{Note that prosumers should divide their assets between multiple anonymous addresses; otherwise, each asset might be traced back to its prosumer based on the amount of energy that it contains.}

>>>>

At this point, the production asset can still be traced back to the prosumer since the ledger is public.
To achieve anonymity, the prosumer uses a \emph{mixing service}, which in practice may be implemented as a decentralized protocol, such as CoinShuffle~\cite{ruffing2014coinshuffle} or Xim~\cite{bissias2014sybil}.
The prosumer transfers the production asset to the mixing service using an \emph{energy and financial transaction} \circled{2}, which is also recorded on the distributed ledger.
In turn, the mixing service transfers the production asset to an \emph{anonymous address} \circled{3}\Aron{We should probably insert a good definition here for readers who are unfamiliar with blockchain transactions.}, which is randomly generated and controlled by the prosumer.
Since the mixing service transfers assets from multiple prosumers to multiple anonymous addresses at the same time, and the anonymous addresses were chosen at random by the prosumers, the assets cannot be traced back to the original prosumers after mixing.\footnote{Note that prosumers should divide their assets between multiple anonymous addresses; otherwise, each asset might be traced back to its prosumer based on the amount of energy that it contains.}

### 2017-06-05 papers/IoT2017/transactions.tex
no message

The ability to specify points or intervals in time is crucial.
For example, control signals specify how the microgrid load should change at certain points in time, energy trades specify when energy will be consumed or produced, etc.
To facilitate processing signals and transactions, we divide time into fixed-length intervals, and specify points or periods in time using these discrete timesteps.
The length of the time interval is determined based on the timing assumptions of the physical power system.
For example, the default length of the time interval may be 4 seconds, which corresponds to how frequently the control signal of the DSO typically changes.

@@

\todo{To address malfunctioning or compromised smart meters, we could also impose a limit on withdrawals.}
A transaction is valid if the following two conditions hold.
\begin{compactitem}
\item The smart meter identified in the transaction has been authorized by a regulatory transaction that was previously recorded on the ledger.
\item The smart meter's signature is valid (for public key, see regulatory transactions).
\end{compactitem}

>>>>

The ability to specify points or intervals in time is crucial.
For example, control signals specify how the microgrid load should change at certain points in time, energy trades specify when energy will be consumed or produced, etc.
To facilitate processing signals and transactions, we divide time into fixed-length intervals, and specify points or periods in time using these discrete timesteps.
The length of the time interval is determined based on the timing assumptions of the physical power system.
For example, the default length of the time interval may be 4 seconds, which corresponds to how frequently the control signal of the DSO typically changes.
\Abhishek{We need to add citation here. I will add that tomorrow.}
\Abhishek{What about the deadline within which the transactions should finish? Do we need to say anything here?}
\Aron{Ideally, we should discuss the timing constraints of the ledger (probably when we introduce it), but we would first need to make space for this discussion.}

@@

\Aron{To address malfunctioning or compromised smart meters, we could also impose a limit on withdrawals.}
A transaction is valid if the following two conditions hold.
\begin{compactitem}
\item The smart meter identified in the transaction has been authorized by a regulatory transaction that was previously recorded on the ledger.
\item The smart meter's signature is valid (for public key, see regulatory transactions).
\end{compactitem}
